---
title: "COVID-19 Resource Gallery"
site: rmdgallery::gallery_site
---

<h1>COVID-19 Resource Gallery</h1>

The goal of this gallery is to show an example of how a page can be created with [R Markdown website](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html) based on [YML metadata](meta/resources.yml) and then converted to static website using R package [**rmdgallery**](https://riccardoporreca.github.io/rmdgallery). See the [ReadMe](https://github.com/miraisolutions/covid-19-gallery) on our github page.

This project collects a number of useful on-line resources (dashboards, web apps, ...) around the COVID-19 pandemic embedded in a common gallery website.


### Global dashboards

This gallery includes the following resources that analyse Covid-19 data globally:

```{r, echo=FALSE}
meta <- rmdgallery::gallery_site_config()$gallery$meta
global_meta <- meta[grepl("^global-", names(meta))]
htmltools::tags$ul(
  lapply(names(global_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(global_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Switzerland

This gallery includes the following resources that analyse Covid-19 Swiss data:


```{r, echo=FALSE}
swiss_meta <- meta[grepl("^switzerland-", names(meta))]
htmltools::tags$ul(
  lapply(names(swiss_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(swiss_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### USA

This gallery includes the following resources that analyse Covid-19 American data:


```{r, echo=FALSE}
usa_meta <- meta[grepl("^usa-", names(meta))]
htmltools::tags$ul(
  lapply(names(usa_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(usa_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Italy

This gallery includes the following resources that analyse Covid-19 Italian data:


```{r, echo=FALSE}
italy_meta <- meta[grepl("^italy-", names(meta))]
htmltools::tags$ul(
  lapply(names(italy_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(italy_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Germany

This gallery includes the following resources that analyse Covid-19 German data:


```{r, echo=FALSE}
germany_meta <- meta[grepl("^germany-", names(meta))]
htmltools::tags$ul(
  lapply(names(germany_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(germany_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### UK

This gallery includes the following resources that analyse Covid-19 data from the United Kingdom:


```{r, echo=FALSE}
uk_meta <- meta[grepl("^uk-", names(meta))]
htmltools::tags$ul(
  lapply(names(uk_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(uk_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### France

This gallery includes the following resources that analyse French Covid-19 data:


```{r, echo=FALSE}
france_meta <- meta[grepl("^france-", names(meta))]
htmltools::tags$ul(
  lapply(names(france_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(france_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Denmark

This gallery includes the following resources that analyse Danish Covid-19 data:


```{r, echo=FALSE}
dk_meta <- meta[grepl("^dk-", names(meta))]
htmltools::tags$ul(
  lapply(names(dk_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(dk_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Austria

This gallery includes the following resources that analyse Danish Covid-19 data:


```{r, echo=FALSE}
austria_meta <- meta[grepl("^austria-", names(meta))]
htmltools::tags$ul(
  lapply(names(austria_meta), function(name) {
    href <- sprintf("%s.html", name)
    with(austria_meta[[name]], {
      htmltools::tags$li(
        htmltools::a(href = href, title),
        "by", author, 
        "[", htmltools::a("source", href = url, target = "_blank", .noWS = "outside"), "]"
      )
    })
  })
)
```

### Contact

If you would like to have more sources listed please open an issue in our [github page](https://github.com/miraisolutions/covid-19-gallery/issues) or contact us at contact@mirai-solutions.com.

To learn how to create a dashboard using R Shiny please see our [workshop page](https://mirai-solutions.ch/services/workshops/). 

